---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# maRsden

<!-- badges: start -->
<!-- badges: end -->

The goal of maRsden is to provide easy access to all data collected at the Marsden Farm Long Term Cropping Systems Research Farm, managed by Dr. Matt Liebman at Iowa State University. 

## Installation

You can install the development version of maRsden using devtools

``` {r}
#devtools::install_github("r-lib/usethis")
```

## Progress

The package currently includes the following data:

1. Weather from [Iowa Mesonet Ames Coop Station](https://mesonet.agron.iastate.edu/) 
  + Historical weather (1987-2018)
  + Data-weather years (1987-2018, will be updated once 2019 ends) 
2. General experiment data
  + mrs_plotkey (each year's plot treatments, 2012-2019)
3. Will Osterholtz (WO) data
  + mrs_cornbio_wo (WO corn biomass data from 2013-2014)
  + mrs_soilh2o_wo (WO soil water data from 2013-2014)
4. My data from 2018-2019
  + mrs_nutrients18 (VN soil nutrients at planting in 2018)
  + mrs_penetrom (VN penetrometer readings 2018-2019)

## Example

If you want to load the corn yield data this will make it much easier. 

```{r ex yield}
#library(maRsden)

# data(mrs_cornyield)
```

Or maybe you want to look at Will Osterholtz's corn biomass data. That's easy!
```{r ex wo}
#data(mrs_cornbio_wo)
```
